### 2023-07-04 paper/sec-dis-pseudodata.tex
sect 2

\subsection{Systematic uncertainties}

>>>>

Finally, we would like to compare the kinematic reach
of the LHC neutrino measurements with respect to that of other experiments.
%
Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF} displays
the kinematic coverage of the FASER$\nu$2 experiment in the $(x,Q^2)$ plane,
same as  Fig.~\ref{fig:error_plot_FASERv2_14} now removing bins
containing less than 30 reconstructed events.
%
It is compared to that of electron-ion collisions
at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
as well as to the kinematic coverage of other available hard-scattering datasets involving
nuclear targets or projectiles.
%
Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
production in proton-lead collisions at the LHC.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
    \centering
    \includegraphics[width = 0.8\textwidth]{plots/Kin_nNNPDF30_EIC_FPF.pdf}
    \caption{The kinematic coverage of the FASER$\nu$2 experiment in the $(x,Q^2)$ plane,
      same as  Fig.~\ref{fig:error_plot_FASERv2_14} now removing bins
      containing less than 30 reconstructed events.
      %
      It is compared to that of electron-ion collisions
      at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
      as well as to the kinematic coverage of other available hard-scattering datasets involving
      nuclear targets or projectiles.
      %
      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
      fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
      production in proton-lead collisions at the LHC.
      }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Systematic uncertainties}
\label{sec:systematic_uncertainties}
